Parsing mPFC: Community analysis

### 2018-08-15 Analyze_summaries.Rmd
Added random ideas for intro

>>>>

### scrabbling
Previous meta analytic studies have provided important insights on the psychological phenomena attributed to mPFC subregions. For example, ADV et al find subdivisions of mPFC and MCC that are significantly tied to decision making in the literature. In particular, they show that more ventral regions are more tightly associated with reward and fear. However, this pattern overlaps with their finding that vmPFC also coactivates with DMN regions, and find no topographical distinction between these phenomena. Similarly, the results from Bartra et al and Laird et al show that this region can't be subdivided into DMN vs subjective value (acikalin, chris, russ). However, meta analysis rely on peaks often derived from group-averaged data. Recent work has prescribed relevance to the analysis of single subjects in fMRI. Yeo et al (2018) propose the use of individualized topologies when identifying functional networks. Gordon et al identify important idiosincrasies in oversampled subjects. Similarly, Braga and Buckner show that finer subdivisions of the DMN are possible when looking at each subject independently. This opens up the possibility that distinctions between DMN and subjective value are possible at this finer level of resolution, but would otherwise be masked in meta analytic work.
Braga & Buckner's work is particularly informative when it comes to subdividing DMN. However, the seed-based functional connectivity analysis is sensitive to the selection of the seed. A natural next step would be to recruit all possible patterns of covariation within this network. A popular alternative is to rely on graph theoretic methods, which provide a characterization of networks that organically fits brain dynamics (provides an organic avenue to understand brain dynamics?), and thus permits the consideration of the full covariance structure of brain networks. (ADV & Tal somewhere here).

add tors work too

It is true that subregions of mPFC can be multifaceted, and ADV et al do suggest that given that no single psych construct belonged to each area. That said, the possibility remains that this is a feature of group averaging.
